---
title: "Data dictionary Crabs"
author: "Barde Julien ,Herinomena Andriamasinoro"
date: "`r Sys.Date()`"
output: 
  html_document:
  toc: true
  theme: united
  number_sections: true
params: 
  gsheet_schemas: "https://docs.google.com/spreadsheets/d/1nXZODXDUsbX2Ht3w-W0DHHn6ZPRKkhmylreIkU_TnI0/edit#gid=1350070480"
  gsheet_tables: "https://docs.google.com/spreadsheets/d/1nXZODXDUsbX2Ht3w-W0DHHn6ZPRKkhmylreIkU_TnI0/edit#gid=896284500"
  gsheet_columns: "https://docs.google.com/spreadsheets/d/1nXZODXDUsbX2Ht3w-W0DHHn6ZPRKkhmylreIkU_TnI0/edit#gid=28130720"
  crabs_schema_db: "https://drive.google.com/file/d/1s0oASwnznZerfperWPtrgW37ClySXLg-/view?usp=sharing"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r}
library(dplyr)
library(knitr)
library(gsheet)
library(kableExtra)
```


```{r}
# https://www.rdocumentation.org/packages/gsheet/versions/0.4.5
df_dwc_gsheet_columns <- as.data.frame(gsheet::gsheet2tbl(params$gsheet_columns))
df_dwc_gsheet_tables <- as.data.frame(gsheet::gsheet2tbl(params$gsheet_tables))
df_dwc_gsheet_schemas <- as.data.frame(gsheet::gsheet2tbl(params$gsheet_schemas))
schemas <- df_dwc_gsheet_schemas %>% select(schema=Schema,description=Definition)
tables <- df_dwc_gsheet_tables %>% select(schema=Schema,table=Table,description=Definition)
columns <- df_dwc_gsheet_columns %>% select(schema=Schema,table=Table,column=Column,description=Definition)
```

# Introduction

This report describes the data dictionary of the "Corecrabe" database. The content is taken from the following google spreadsheets :  

* [List of colums for all schemas](`r params$gsheet_schemas`)
* [List of colums for all tables](`r params$gsheet_tables`)
* [List of colums for all columns](`r params$gsheet_columns`)

The content of the data dictionnary can be improved by editing the google spreadsheets.

![Database schema of raw GPS data](`r params$crabs_schema_db`){width=40%} !
 



# The schemas

Here is the list and definition of schemas in the database

```{r echo = FALSE, results = 'asis'}
kable(schemas, caption = "Description of schemas") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


# The tables


```{r echo = FALSE, results = 'asis'}
kable(tables, caption = "Description of tables") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


# The columns


```{r echo = FALSE, results = 'asis'}
kable(columns, caption = "Description of columns") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


# References

The script to generate this report is available [here](https://github.com/juldebar/MIKAROKA/blob/main/Rmd/data-dictionary-crabs.Rmd)