---
title: "Data dictionary invertebre sarodrano"
author: "Herinomena Andriamasinoro, Julien bard"
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: true
    toc: true
    theme: united
    number_sections: true
params: 
  gsheet_tables: "https://docs.google.com/spreadsheets/d/1OL6hwzyX0yYpy119oIEC2LeXBkbnnbd1fyROMBNFJYM/edit#gid=932678001"
  gsheet_columns: "https://docs.google.com/spreadsheets/d/1OL6hwzyX0yYpy119oIEC2LeXBkbnnbd1fyROMBNFJYM/edit?usp=sharing"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library(dplyr)
library(knitr)
library(gsheet)
library(kableExtra)
```


```{r}
df_dwc_gsheet_columns <- as.data.frame(gsheet::gsheet2tbl(params$gsheet_columns))
df_dwc_gsheet_tables <- as.data.frame(gsheet::gsheet2tbl(params$gsheet_tables))

tables <- df_dwc_gsheet_tables %>% select(table=Table,description=Definition)
columns <- df_dwc_gsheet_columns %>% select(table=Table,column=Column,description=Definition)
```

# Introduction

This report describes the data dictionary for the "sarodrano invertebrate" data. The contents are taken from the following Google spreadsheets:

* [List of colums for all tables](`r params$gsheet_tables`)
* [List of colums for all columns](`r params$gsheet_columns`)

The content of the data dictionnary can be improved by editing the google spreadsheets.



# The tables

Here is the list and definition of tables in the data

```{r echo = FALSE, results = 'asis'}
kable(tables, caption = "Description of tables") %>%
kable_styling(bootstrap_options = c("striped", "hover"))
```

# The columns


```{r echo = FALSE, results = 'asis'}
kable(columns, caption = "Description of columns") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# References

The script to generate this report is available [here](https://github.com/juldebar/MIKAROKA/blob/main/Rmd/Data_dictionary_invertebre_sarodrano.Rmd)
